\chapter*{Abbreviations}\label{abbr}

\begin{description}
	\item[AJAX] \hfill \\ \underline{A}synchronous \underline{Ja}vaScript and \underline{X}ML describes a way to send data to and retrieve data from a server asynchronously (in the background), so the GUI is not blocking.
	\item[API\label{API}] \hfill \\ An \underline{A}pplication \underline{P}rogramming \underline{I}nterface specifies how software components interact with each other.
	\item[B2B] \hfill \\ \underline{B}usiness \underline{t}o \underline{B}usiness communication usually describes the way software of two different companies talk to each other.
	\item[ECG\label{ECG}] \hfill \\ \underline{E}lectro\underline{C}ardio\underline{G}ram (also known as EKG) is a recording procedure used for analysing the patient`s electrical heart activity over time.
	\item[ER diagram\label{ERdiagram}] \hfill \\ \underline{E}ntity \underline{R}elationship model is a data model for describing a data model in an abstract way.
	\item[GUI\label{GUI}] \hfill \\ \underline{G}raphical \underline{U}ser \underline{I}nterface is a visual way of interacting with a computer using items such as windows, icons, and menus, used by most modern operating systems.
	\item[HTTPS\label{HTTP}] \hfill \\ \underline{H}yper\underline{t}ext \underline{T}ransport \underline{P}rotocol \underline{S}ecure is the secure version of the HTTP protocol used in the World Wide Web.
	\item[REST\label{REST}] \hfill \\ \underline{Re}presentational \underline{S}tate \underline{T}ransfer is an architeture style for distributed systems developed by World Wide Web Consortium (W3C). The Internet is the largest implementation of the architecture.
\end{description}
